Postural developments mediate children's visual access to social information

### 2018-01-26 writeup-cogsci/cogsci2018_faceOnly.Rmd
add feather call

```{r, libraries}
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(xtable)
library(lubridate)
library(langcog)
library(ggplot2)
library(ggthemes)
library(egg) # plot arranging
library(lme4)
library(gridExtra)
```
# Introduction

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}
### READ IN DETECTIONS
d <- read_csv("../data/consolidateddata/consolidated_data_4detectors.csv") %>%
  mutate(posture = factor(posture), orientation = factor(orientation))

>>>>

```{r, libraries}
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(xtable)
library(lubridate)
library(langcog)
library(ggplot2)
library(ggthemes)
library(egg) # plot arranging
library(lme4)
library(gridExtra)
library(feather)
```
# Introduction

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}
### READ IN DETECTIONS
getwd()
d <- read_feather("../data/consolidated_data_4detectors.feather") %>%
  mutate(posture = factor(posture), orientation = factor(orientation))
